Delay Comparison of Different Switch Architectures

### 2013-11-10 MSReport/MSThesis.tex
started describing events

>>>>

\subsubsection{Events}

All changes to the state occur through the application of an Event object to the state through the update$\_$state() function.  So essentially, an Event object consists of three things: the change to be applied to the state, the time at which it occurs, and a merge() function, to calculate a new Event from two candidate Events.  Of these three things, the merge() is the only one which is the least straightforward:
\begin{verbatim}
Event merge(event)
{
     if(event occurs before this)
     {
          return event
     }
     if(event occurs after this)
     {
           return this
     }
     if(event occurs simultaneously with this)
     {
            include both state changes
            return this
     }
}
\end{verbatim}

Given this structure the next$\_$event() function is philosophically structured as follows:

\begin{verbatim}
Event next_event()
{
     event = next_pkt_gen()
     event.merge(next_nic_update())
     event.merge(next_crossbar_update())
     event.merge(event_heap.next_ack())
     return event
}
\end{verbatim}

Notice that there is no effort to save the events that merge discards.  This is because the stochastic events are generated in a memoryless fashion parametrized by the state (i.e. either occur or do not with the same probability at each time step).  The deterministic events are all a function of the state and can be recalculated from the new state that results after the application of an earlier event.  The ACKs are stored in the event$\_$heap, but could in theory also have their own state variable.  Other deterministic events could also be stored in the event$\_$heap if the depending on the preference of the coder.
